---
title: "GCDS Final"
author: "ktsai, Brian, Rebecca"
date: "2022-11-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

# **DATA PREPARATION**

## General Game Survey

### *Cleaning/Tidying Data*

Step 1. Read the .csv into an object  
Step 2. Filter out bad/incomplete data (i.e., invalid IDs, all of which are <1910; the unfinished responses)  
Step 3. Select only relevant columns (i.e., code ID and Game variables)  
Step 4. Convert all '99' error values into NAs

```{r GS: Data Cleaning}
# General Survey, cleaned (GS)
GS <- readr::read_csv("GCDS22_11-15_numeric.csv")

GS <- GS %>% 
  filter(code < 1910, Finished == 1) %>%
  select(-c(1:17), -id) %>%
  mutate(across(.fns = ~na_if(.,99)))

```

### *Gathering continuous variables for clustering*

We filter out the binary outcome variables (All the Pleasure__1:Pleasure__10 and Design_1:PLAY variables)   from GS and create a new DF called GS_c. This prepares the data for clustering.

```{r GS: selecting continuous variables }
# General Survey w/ only continuous variables (GS_c)
GS_c <- GS %>% 
  select(!c(Pleasure__1:Pleasure__11, Design_1:PLAY)) 

```


## Individual post-gameplay responses

### *Cleaning/Tidying Data*

Step 1. Read game csv into an object  
Step 2. filter out invalid codes  
Step 3. Select only relevant columns (i.e., code ID and response variables)  

```{r Individual Games}
# Love Letter (LL)
LL <- readr::read_csv("LoveLetter_11-15_numeric.csv")

LL <- LL %>%
  filter(code < 1910) %>% 
  select(-c(1:17))

# Taco Cat Goat Cheese Pizza (TC)
TC <- readr::read_csv("TacoCat_11-15_numeric.csv")

TC <- TC %>%
  filter(code < 1910) %>% 
  select(-c(1:17))

```


