---
title: "GCDS Final"
author: "Kayleah, Brian, Rebecca"
date: "2022-11-17"
output: html_document
---
```{r}
rm(list = ls(all.names = TRUE))      # remove objects in R
source("https://pastebin.com/raw/8mXH02yg")   # run and comment out after knitting
source("https://pastebin.com/raw/97NNTTzu")   # run to include in function definitions
# set the paths for project, script, and data dirs
proj_dir <- gsub("GCDS.*.Rmd", "GCDS", get_ActivePath())
proj_name = ""
r_dir    <- paste(proj_dir, "r", sep = "/")    # r subdir
data_dir <- paste(proj_dir, "data", sep = "/") # data subdir
if ( proj_name != "" & !dir.exists(paste(proj_dir, proj_name, sep = "/")) ) {
# create project dir
suppressWarnings(dir.create(paste(proj_dir, proj_name, sep = "/")))
r_dir <- gsub("/r", paste0("/", proj_name, "/r"), r_dir)
data_dir <- gsub("/data", paste0("/", proj_name, "/data"), data_dir)
# create sub directories
suppressWarnings(dir.create(r_dir))
suppressWarnings(dir.create(data_dir)) }
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

# **DATA PREPARATION**

## General Game Survey

### *Cleaning/Tidying Data*

1. Read the .csv into an object  
2. Filter out bad/incomplete data (i.e., the invalid 99999 id and the unfinished responses)  
3. Select only relevant columns (i.e., code ID and Game variables)  
4. Convert all '99' error values into NAs

```{r GS: Data Cleaning}
# General Survey, cleaned (GS)
GS <- readr::read_csv("GCDS22_11-15_numeric.csv")

GS <- GS %>% 
  filter(code < 2100, Finished == 1) %>%
  select(-c(1:17), -id) %>%
  mutate(across(.fns = ~na_if(.,99)))

```

### *Gathering continuous variables for clustering*

We filter out the binary outcome variables (All the Pleasure__1:Pleasure__10 and Design_1:PLAY variables)   from GS and create a new DF called GS_c. This prepares the data for clustering.

```{r GS: selecting continuous variables }
# General Survey w/ only continuous variables (GS_c)
GS_c <- GS %>% 
  select(!c(Pleasure__1:Pleasure__11, Design_1:PLAY)) 

GS_c <- na.omit(GS_c)

```


## Individual post-gameplay responses

### *Cleaning/Tidying Data*

1. Read game csv into an object  
2. Slice out the rows that aren't participant data   
3. Select only relevant columns (i.e., code ID and response variables)  

```{r Individual Games}
# Love Letter (LL)
LL <- readr::read_csv("LoveLetter_11-15_numeric.csv")

LL <- LL %>%
  slice(3:42) %>% 
  select(-c(1:17))

# Taco Cat Goat Cheese Pizza (TC)
TC <- readr::read_csv("TacoCat_11-15_numeric.csv")

TC <- TC %>%
  slice(3:37) %>% 
  select(-c(1:17))

```

# **Clustering**

## General Game Survey

### *K-means clustering on the General Game Survey*

```{r}
# Compute k-means with k = 4
set.seed(123)
km.res <- kmeans(GS_c, 2, nstart = 10)


# Print the results
view(km.res)


```



